{[}

### 2006-06-12 BD_radvel/tmp.tex
New RV measurements. Revisions done.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@740 25464f21-6099-402c-b30a-640f1d40d38b

%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[oneside,english,useAMS, usenatbib]{mn2e}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Bold symbol macro for standard LaTeX users
\newcommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{times}
\usepackage{amssymb}

@@

\newcommand{\kmps}{\mathrm{km~s^{-1}}}
\newcommand\ion[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
\newcommand{\Kelvin}{\mathrm{K}}
\newcommand{\Msun}{\mathrm{M_{\odot}}}

\usepackage{babel}
\makeatother
\begin{document}
\title[Radial and rotational velocities of young BDs and VLM stars]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core}

\author[R. Kurosawa et\,al.]{Ryuichi
  Kurosawa$^1$\thanks{E-mail:rk@astro.ex.ac.uk}, Tim J. Harries$^1$
  and S.~P.~Littlefair$^2$\\ $^1$School of Physics, University of
  Exeter, Stocker Road, Exeter EX4~4QL. \\ $^2$Department of Physics
  and Astronomy, University of Sheffield, Sheffield S3 7RH}

@@

\maketitle

@@

We present the results of a radial velocity (RV) survey of 14 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi dark
cloud core. We obtained high-resolution echelle spectra at the VLT using
Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
epochs for each object, and measured the shifts in their RVs to
identify candidates for binary/multiple systems in the sample. The
average time separation of the RV measurements is 21.6~d, and our
survey is sensitive to the binaries with separation $<0.1$~au.  We
found 4 out of 17 objects (or $24^{+16}_{-13}$~per~cent by fraction)
show a significant RV change in 4--33~d time scale, and are 
considered as binary/multiple `candidates.'  We found no double-lined
spectroscopic binaries in our sample, based on the shape of
cross-correlation curves. The RV dispersion of the objects in UScoOB
is found to be very similar to that of the BD and VLM stars in
Chamaeleon~I (Cha~). We also found the distribution of the mean
rotational velocities ($v\,\sin i$) of the 
UScoOB objects is similar to that of the Cha~I, but the dispersion of
$v\,\sin i$ is much larger than that of the Cha~I objects.

@@

\begin{center}

\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}

\end{center}

@@

\begin{center}

\begin{tabular}{lcrrrrr}
\hline 
Object&
Date&
HJD-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$\tabularnewline
\hline 
GY 5&
2004-Apr-24&
20.7198440&
$-6.14\pm0.84$&
0.68&
&
\tabularnewline
&
2004-May-07&
33.7721938&
$-5.96\pm0.60$&
0.34&
$-6.05\pm1.03$&
$16.5\pm0.6$\tabularnewline
GY 141&
2004-May-10&
36.6712108&
$-4.39\pm0.60$&
0.34&
&
\tabularnewline
&
2004-May-17&
43.6683007&
$-2.95\pm0.51$&
0.11&
$-3.67\pm0.79$&
$4.4\pm1.4$\tabularnewline
GY 310&
2004-Apr-24&
20.8373504&
$-4.83\pm0.74$&
0.54&
&
\tabularnewline
&
2004-May-09&
35.8224052&
$-8.43\pm0.51$&
0.11&
$-6.63\pm0.90$&
$11.1\pm6.0$\tabularnewline
USco 40&
2004-Apr-05&
1.7661754&
$-7.15\pm0.74$&
0.54&
&
\tabularnewline
&
2004-May-07&
33.7620554&
$-6.80\pm0.51$&
0.11&
$-6.98\pm0.90$&
$34.2\pm0.5$\tabularnewline
USco 53&
2004-Apr-04&
0.9036653&
$-7.27\pm0.93$&
1.21&
&
\tabularnewline
&
2004-May-02&
28.7394676&
$-5.43\pm0.74$&
0.55&
$-6.35\pm1.19$&
$40.0\pm0.6$\tabularnewline
USco 55&
2004-Apr-05&
1.8422807&
$-5.39\pm0.50$&
0.02&
&
\tabularnewline
&
2004-May-02&
28.8141198&
$-6.38\pm0.53$&
0.27&
$-6.38\pm0.73$&
$22.9\pm0.8$\tabularnewline
USco 66&
2004-Apr-05&
1.7972634&
$-5.32\pm0.57$&
0.29&
&
\tabularnewline
&
2004-May-02&
28.7956003&
$-6.41\pm0.65$&
0.42&
$-5.87\pm0.86$&
$25.9\pm1.2$\tabularnewline
USco 67&
2004-Apr-05&
1.7188620&
$-6.01\pm0.74$&
0.55&
&
\tabularnewline
&
2004-May-02&
28.7113799&
$-6.83\pm0.59$&
0.31&
$-6.42\pm0.90$&
$18.4\pm0.4$\tabularnewline
USco 75&
2004-Apr-04&
0.8840376&
$-6.75\pm0.67$&
0.44&
&
\tabularnewline
&
2004-May-07&
33.6065432&
$-9.88\pm1.94$&
1.88&
$-8.32\pm2.05$&
$55.6\pm3.0$\tabularnewline
USco 100&
2004-Apr-06&
1.8179138&
$-6.76\pm2.74$&
2.69&
&
\tabularnewline
&
2004-May-02&
28.7752928&
$-10.23\pm1.80$&
1.73&
$-8.47\pm3.28$&
$43.7\pm3.2$\tabularnewline
USco 101&
2004-Apr-04&
0.8120734&
$-4.22\pm0.87$&
0.71&
&
\tabularnewline
&
2004-May-02&
28.6591660&
$-6.07\pm0.69$&
0.48&
$-5.15\pm1.11$&
$19.1\pm0.3$\tabularnewline
USco 104&
2004-Apr-04&
0.7850385&
$-5.83\pm0.50$&
0.02&
&
\tabularnewline
&
2004-May-02&
28.6349480&
$-7.48\pm0.50$&
0.06&
$-6.66\pm0.06$&
$16.7\pm0.4$\tabularnewline
USco 109&
2004-Apr-05&
1.7453989&
$-4.15\pm0.52$&
0.16&
&
\tabularnewline
&
2004-May-07&
33.6304878&
$-4.41\pm0.50$&
0.03&
$-5.12\pm0.72$&
$8.6\pm1.2$\tabularnewline
USco 112&
2004-Apr-04&
0.8552168&
$-2.70\pm0.69$&
0.47&
&
\tabularnewline
&
2004-May-07&
33.5826368&
$-3.46\pm0.51$&
0.11&
$-3.08\pm0.86$&
$5.8\pm1.2$\tabularnewline
USco 121&
2004-Apr-24&
20.7059408&
$-39.47\pm0.51$&
0.11&
&
\tabularnewline
&
2004-May-02&
28.6969641&
$-42.43\pm0.50$&
0.02&
$-40.95\pm0.71$&
$17.6\pm1.3$\tabularnewline
USco 128&
2004-May-13&
39.7978276&
$-7.41\pm0.85$&
0.69&
&
\tabularnewline
&
2004-May-17&
43.6108024&
$-6.94\pm1.16$&
1.05&
$-7.18\pm1.44$&
$3.6\pm1.1$\tabularnewline
USco 130&
2004-May-09&
35.7724090&
$-4.83\pm0.54$&
0.21&
&
\tabularnewline
&
2004-May-13&
39.8538830&
$-4.95\pm0.74$&
0.55&
$-4.89\pm0.92$&
$15.2\pm1.1$\tabularnewline
USco 132&
2004-May-13&
39.8268683&
$-7.18\pm0.58$&
0.30&
&
\tabularnewline
&
2004-May-17&
43.6391138&
$-7.37\pm1.02$&
0.89&
$-7.28\pm1.17$&
$9.1\pm0.7$\tabularnewline
\hline
\end{tabular}

\end{center}

@@

\begin{center}

\includegraphics[%
  clip,
  scale=1.3]{figures/radvel_all01.eps}

\end{center}

\caption{Relative radial velocities (RVs) of objects measured in two
different epochs. The vertical axes indicate the amount of deviation
($\Delta \mathrm{RV}$) from the `average' radial velocity
($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and
the horizontal axes indicate the time of the observation in
heliocentric Julian date (HJD). The objects are considered to have a
non-constant RV when the error bars of two data points do not overlap
each other. The non-constant RV objects are considered as
binary/multiple candidates.}

@@

\begin{center}

\includegraphics[%
  clip,
  scale=1.3]{figures/radvel_all02.eps}

\end{center}

@@

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. 
To determine the $\sigma_{\mathrm{RRV}}$, we have used the following
procedure: (1)~add random gaussian deviate noise to the object spectra using the
corresponding variance spectra, (2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by location the peak, (4)~repeat 1--3 for 100 times, and computes the standard
deviation of the 100 RV values. This should provide a good estimate of
uncertainties in RV cased by the uncertainties in the flux levels.
%The two consecutive measurements of RVs (from same nights) are used to
%find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
%the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
%the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
Note that for finding a shift in the radial velocities from two
different epochs, only $\sigma_{\mathrm{RRV}}$ is important since one
only requires relative (with respect to a template) RV values.
The `average' radial velocities $\left (\overline{\mathrm{RV}} \right )$ of the
two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.

@@

\begin{center}
\includegraphics[%
  clip,
  scale=0.63]{figures/chisq_hist.eps}
\end{center}

\caption{Histogram of the $\chi^2$ probability ($p$) for fitting the
  observed (relative) RV values with a constant (a horizontal
  line). The constant used in the fit is determined from the weighted mean of
  the two RV measurements for each object.  The objects with
  $p<10^{-3}$ are identified as \emph{non-constant} or \emph{multiple},
  which appear in the right-most bin in the histogram. There
  are four objects which satisfy this condition. The
  expected distribution (dashed) for RV constant objects based on the RV
  uncertainties in the observations (Table~\ref{tab:summary_results})
  and based on the $\chi^{2}$ probability function is also shown for a
  comparison.  The match between the expected distribution and the
  histogram is reasonable, indicating that our uncertainty estimates
  in RV values are also reasonable.  }

@@

\begin{center}

\includegraphics[%
  clip,
  scale=0.63]{figures/radvel_hist.eps}

\end{center}

\caption{Histogram of the average heliocentric radial velocities of 14 UScoOB BD and VLM
objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
a non-member). The gaussian fit (dashed) of the radial velociity
distribution gives a standard deviation of $1.2\,\kmps$ and the peak
position of $-5.9\,\kmps$. }
\label{fig:vrad_histrogram}

@@

\begin{center}

\includegraphics[%
  clip,
  scale=0.63]{figures/vrot_hist.eps}

\end{center}

\caption{Histogram of the rotational velocities ($v\,\sin{i}$) of 14 UScoOB BD and VLM
objects listed in Table~\ref{tab:summary_results} (excluding USco~121,
a non-member).  The log-normal fit (dashed) of the
rotational velocity distribution gives a standard deviation
$27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
\label{fig:vrot_histrogram}

@@

\section{Binary fraction}
\label{sec:Binary-fraction}

In Section~\ref{sub:Radial-velocities}, we found 4 out of 17
(excluding USco~121; non-member) objects show a statistically
significant RV variation, indicating that they are binary/multiple
candidates. In order to estimate the uncertainty in the
binary/multiple fraction from this relatively small sample, we will
follow the method used by \citet{basri:2006} who considered the binomial
distribution, $P_{B}\left ( x, n, p \right )$ of $x$ positive event
out of $n$ trials with the probability $p$ for a positive event in each
trial. In our case, $n=17$ (the number of sample) and $x=4$.  The peak
of $P_{B}\left ( 4, 17, p \right )$ curve suggests the binary fraction of
24~per~cent, as its should be ($4/17=0.24$).  The uncertainties was estimated by
plotting $P_{B}\left ( 4, 17, p \right )$, and finding the values
of $p$ at which $P_{B}$ reduced to $e^{-1}$ of the peak value.  In this
analysis, we find the binary/multiple fraction along with the
uncertainties of our sample to be $f=24^{+16}_{-13}$~per~cent.

@@

%

%

>>>>

%% LyX 1.4.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[onecolumn,english,oneside,useAMS, usenatbib]{mn2e}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Bold symbol macro for standard LaTeX users
\providecommand{\boldsymbol}[1]{\mbox{\boldmath $#1$}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%% LyX 1.3 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Bold symbol macro for standard LaTeX users

%% Because html converters don't know tabularnewline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{times}

@@

\newcommand{\kmps}{\mathrm{km~s^{-1}}}
\newcommand{\ion}[2]{#1$\,${\sc {#2}}}   % ion, i.e., CII = \ion{C}{ii}
\newcommand{\Kelvin}{\mathrm{K}}
\newcommand{\Msun}{\mathrm{M_{\odot}}}

\makeatother

\usepackage{babel}
\makeatother
\begin{document}

\title{{[}}

\maketitle
Radial and rotational velocities of young BDs and VLM stars]{Radial
and rotational velocities of young brown dwarfs and very low-mass
stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi
cloud core}

\author{{[}}

R. Kurosawa et\,al.]{Ryuichi Kurosawa$^{1}$\thanks{E-mail:rk@astro.ex.ac.uk},
Tim J. Harries$^{1}$ and S.~P.~Littlefair$^{2}$\\
 $^{1}$School of Physics, University of Exeter, Stocker Road, Exeter
EX4~4QL. \\
 $^{2}$Department of Physics and Astronomy, University of Sheffield,
Sheffield S3 7RH}

@@

@@

We present the results of a radial velocity (RV) survey of 14 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi
dark cloud core. We obtained high-resolution echelle spectra at the
VLT using Ultraviolet and Visual Echelle Spectrograph (UVES) at two
different epochs for each object, and measured the shifts in their
RVs to identify candidates for binary/multiple systems in the sample.
The average time separation of the RV measurements is 21.6~d, and
our survey is sensitive to the binaries with separation $<0.1$~au.
We found 4 out of 17 objects (or $24_{-13}^{+16}$~per~cent by fraction)
show a significant RV change in 4--33~d time scale, and are considered
as binary/multiple `candidates.' We found no double-lined spectroscopic
binaries in our sample, based on the shape of cross-correlation curves.
The RV dispersion of the objects in UScoOB is found to be very similar
to that of the BD and VLM stars in Chamaeleon~I (Cha~). We also
found the distribution of the mean rotational velocities ($v\,\sin i$)
of the UScoOB objects is similar to that of the Cha~I, but the dispersion
of $v\,\sin i$ is much larger than that of the Cha~I objects.

@@

\begin{center}\begin{tabular}{llcccc}
\hline 
Object&
Sp.&
mass&
RV&
$v\sin i$&
Known multiple?\tabularnewline
&
&
$\left[\mathrm{M_{\odot}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
\tabularnewline
\hline 
GY 5&
$\mathrm{M7^{c}}$&
$0.07^{\mathrm{d}}$&
$-6.3\pm1.9^{\mathrm{d}}$&
$16.8\pm2.7^{\mathrm{d}}$&
no\tabularnewline
GY 141&
$\mathrm{M8.5^{a}}$&
$0.02^{\mathrm{d}}$&
\ldots{}&
$6.0^{f}$&
no\tabularnewline
GY 310&
$\mathrm{M8.5^{c}}$&
$0.08^{\mathrm{a,d}}$&
\ldots{}&
$10.0^{f}$&
no\tabularnewline
USco 40&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$37.5^{f}$&
no\tabularnewline
USco 53&
$\mathrm{M5^{b}}$&
$0.1^{\mathrm{b}}$&
\ldots{}&
$45.0^{f}$&
no\tabularnewline
USco 55&
$\mathrm{M5.5^{b}}$&
$0.10+0.07^{\mathrm{e}}$&
\ldots{}&
$12.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 66&
$\mathrm{M6^{b}}$&
$0.07+0.07^{\mathrm{e}}$&
$-4.4\pm0.6^{\mathrm{d}}$&
$27.5^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 67&
$\mathrm{M5.5^{b}}$&
$0.10^{\mathrm{e}}$&
\ldots{}&
$18.0^{f}$&
no\tabularnewline
USco 75&
$\mathrm{M6^{b}}$&
$0.07^{\mathrm{e}}$&
$-5.6\pm1.1^{\mathrm{d}}$&
$63.0^{f}$&
no\tabularnewline
USco 100&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.9\pm0.6^{\mathrm{d}}$&
$50.0^{f}$&
no\tabularnewline
USco 101&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
\ldots{}&
no\tabularnewline
USco 104&
$\mathrm{M5^{b}}$&
$0.05^{\mathrm{b}}$&
\ldots{}&
$16.0^{f}$&
no\tabularnewline
USco 109&
$\mathrm{M6^{b}}$&
$0.07+0.04^{\mathrm{e}}$&
$-3.8\pm0.7^{\mathrm{d}}$&
$6.0^{f}$&
$\mathrm{visual^{e}}$\tabularnewline
USco 112&
$\mathrm{M5.5^{b}}$&
$0.1^{\mathrm{e}}$&
\ldots{}&
$8.0^{f}$&
no\tabularnewline
USco 121&
$\mathrm{M6^{b}}$&
$0.02^{\mathrm{b}}$&
$-38.9\pm1.0^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
USco 128&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-3.0\pm1.6^{\mathrm{d}}$&
$0.0^{f}$&
no\tabularnewline
USco 130&
$\mathrm{M7.5^{e}}$&
$0.04^{\mathrm{e}}$&
\ldots{}&
$14.0^{f}$&
no\tabularnewline
USco 132&
$\mathrm{M7^{b}}$&
$0.05^{\mathrm{e}}$&
$-8.2\pm1.1^{\mathrm{d}}$&
\ldots{}&
no\tabularnewline
\hline
\end{tabular}\par\end{center}

@@

\begin{center}\begin{tabular}{lcrrrrr}
\hline 
0.81&
Date&
HJD-2453100&
RV&
$\sigma_{\mathrm{RRV}}$&
$\overline{\mathrm{RV}}$&
$v\sin i$\tabularnewline
&
&
&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$&
$\left[\mathrm{km\, s^{-1}}\right]$\tabularnewline
\hline 
GY 5&
2004-Apr-24&
20.7198440&
$-6.77\pm2.02$&
1.96&
&
\tabularnewline
&
2004-May-07&
33.7721938&
$-6.02\pm0.85$&
0.68&
$-6.39\pm2.19$&
$16.5\pm0.6$\tabularnewline
GY 141&
2004-May-10&
36.6712108&
$-4.15\pm0.63$&
0.38&
&
\tabularnewline
&
2004-May-17&
43.6683007&
$-3.46\pm0.66$&
0.43&
$-3.81\pm0.91$&
$4.4\pm1.4$\tabularnewline
GY 310&
2004-Apr-24&
20.8373504&
$-5.27\pm0.92$&
0.77&
&
\tabularnewline
&
2004-May-09&
35.8224052&
$-8.19\pm0.71$&
0.51&
$-6.73\pm1.16$&
$11.1\pm6.0$\tabularnewline
USco 40&
2004-Apr-05&
1.7661754&
$-7.34\pm0.52$&
0.15&
&
\tabularnewline
&
2004-May-07&
33.7620554&
$-6.28\pm0.52$&
0.15&
$-6.81\pm0.74$&
$34.2\pm0.5$\tabularnewline
USco 53&
2004-Apr-04&
0.9036653&
$-8.27\pm0.70$&
0.50&
&
\tabularnewline
&
2004-May-02&
28.7394676&
$-7.22\pm0.63$&
0.39&
$-7.75\pm0.95$&
$40.0\pm0.6$\tabularnewline
USco 55&
2004-Apr-05&
1.8422807&
$-6.21\pm0.50$&
0.04&
&
\tabularnewline
&
2004-May-02&
28.8141198&
$-6.55\pm0.50$&
0.06&
$-6.38\pm0.71$&
$22.9\pm0.8$\tabularnewline
USco 66&
2004-Apr-05&
1.7972634&
$-7.24\pm0.95$&
0.81&
&
\tabularnewline
&
2004-May-02&
28.7956003&
$-8.38\pm1.32$&
1.22&
$-7.81\pm1.63$&
$25.9\pm1.2$\tabularnewline
USco 67&
2004-Apr-05&
1.7188620&
$-7.07\pm0.67$&
0.44&
&
\tabularnewline
&
2004-May-02&
28.7113799&
$-5.70\pm0.58$&
0.30&
$-6.38\pm0.88$&
$18.4\pm0.4$\tabularnewline
USco 75&
2004-Apr-04&
0.8840376&
$-6.80\pm0.70$&
0.50&
&
\tabularnewline
&
2004-May-07&
33.6065432&
$-6.16\pm0.78$&
0.60&
$-6.48\pm1.05$&
$55.6\pm3.0$\tabularnewline
USco 100&
2004-Apr-06&
1.8179138&
$-7.37\pm0.67$&
0.44&
&
\tabularnewline
&
2004-May-02&
28.7752928&
$-7.47\pm0.62$&
0.36&
$-7.42\pm0.91$&
$43.7\pm3.2$\tabularnewline
USco 101&
2004-Apr-04&
0.8120734&
$-3.25\pm0.66$&
0.44&
&
\tabularnewline
&
2004-May-02&
28.6591660&
$-5.03\pm0.60$&
0.32&
$-4.14\pm0.89$&
$19.1\pm0.3$\tabularnewline
USco 104&
2004-Apr-04&
0.7850385&
$-7.05\pm0.61$&
0.35&
&
\tabularnewline
&
2004-May-02&
28.6349480&
$-7.62\pm0.57$&
0.27&
$-7.33\pm0.83$&
$16.7\pm0.4$\tabularnewline
USco 109&
2004-Apr-05&
1.7453989&
$-4.72\pm0.50$&
0.07&
&
\tabularnewline
&
2004-May-07&
33.6304878&
$-4.70\pm0.51$&
0.09&
$-4.71\pm0.72$&
$8.6\pm1.2$\tabularnewline
USco 112&
2004-Apr-04&
0.8552168&
$-2.95\pm0.50$&
0.05&
&
\tabularnewline
&
2004-May-07&
33.5826368&
$-3.41\pm0.51$&
0.07&
$-3.18\pm0.71$&
$5.8\pm1.2$\tabularnewline
USco 121&
2004-Apr-24&
20.7059408&
$-40.76\pm0.90$&
0.74&
&
\tabularnewline
&
2004-May-02&
28.6969641&
$-42.48\pm0.54$&
0.20&
$-41.62\pm1.04$&
$17.6\pm1.3$\tabularnewline
USco 128&
2004-May-13&
39.7978276&
$-7.03\pm0.51$&
0.09&
&
\tabularnewline
&
2004-May-17&
43.6108024&
$-6.32\pm0.51$&
0.10&
$-6.68\pm0.72$&
$3.6\pm1.1$\tabularnewline
USco 130&
2004-May-09&
35.7724090&
$-3.92\pm0.94$&
0.80&
&
\tabularnewline
&
2004-May-13&
39.8538830&
$-3.90\pm0.67$&
0.45&
$-3.91\pm1.16$&
$15.2\pm1.1$\tabularnewline
USco 132&
2004-May-13&
39.8268683&
$-6.68\pm0.53$&
0.18&
&
\tabularnewline
&
2004-May-17&
43.6391138&
$-6.61\pm0.54$&
0.20&
$-6.64\pm0.76$&
$9.1\pm0.7$\tabularnewline
\hline
\end{tabular}\par\end{center}

@@

\begin{center}\includegraphics[clip,scale=1.3]{figures/radvel_all01}\par\end{center}

\caption{Relative radial velocities (RVs) of objects measured in two different
epochs. The vertical axes indicate the amount of deviation ($\Delta\mathrm{RV}$)
from the `average' radial velocity ($\overline{\mathrm{RV}}$) in
Table~\ref{tab:summary_results}), and the horizontal axes indicate
the time of the observation in heliocentric Julian date (HJD). The
objects are considered to have a non-constant RV when the error bars
of two data points do not overlap each other. The non-constant RV
objects are considered as binary/multiple candidates.}

@@

\begin{center}\includegraphics[clip,scale=1.3]{figures/radvel_all02}\par\end{center}

@@

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. To determine
the $\sigma_{\mathrm{RRV}}$, we have used the following procedure:
(1)~add random gaussian deviate noise to the object spectra using
the corresponding variance spectra, (2)~compute the cross-correlation
curve using the spectra with added noise and the template, (3)~measure
the RV by location the peak, (4)~repeat 1--3 for 100 times, and computes
the standard deviation of the 100 RV values. This should provide a
good estimate of uncertainties in RV cased by the uncertainties in
the flux levels. %The two consecutive measurements of RVs (from same nights) are used to
%find the (absolute/heliocentric) RV of the night, and their uncertainties are obtained from
%the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
%the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
Note that for finding a shift in the radial velocities from two different
epochs, only $\sigma_{\mathrm{RRV}}$ is important since one only
requires relative (with respect to a template) RV values. The `average'
radial velocities $\left(\overline{\mathrm{RV}}\right)$ of the two
epochs are also given in the same table. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}.

@@

\begin{center}\includegraphics[clip,scale=0.63]{figures/chisq_hist} \par\end{center}

\caption{Histogram of the $\chi^{2}$ probability ($p$) for fitting the observed
(relative) RV values with a constant (a horizontal line). The constant
used in the fit is determined from the weighted mean of the two RV
measurements for each object. The objects with $p<10^{-3}$ are identified
as \emph{non-constant} or \emph{multiple}, which appear in the right-most
bin in the histogram. There are four objects which satisfy this condition.
The expected distribution (dashed) for RV constant objects based on
the RV uncertainties in the observations (Table~\ref{tab:summary_results})
and based on the $\chi^{2}$ probability function is also shown for
a comparison. The match between the expected distribution and the
histogram is reasonable, indicating that our uncertainty estimates
in RV values are also reasonable. }

@@

\begin{center}\includegraphics[clip,scale=0.63]{figures/radvel_hist}\par\end{center}

\caption{Histogram of the average heliocentric radial velocities of 14 UScoOB
BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding
USco~121, a non-member). The gaussian fit (dashed) of the radial
velociity distribution gives a standard deviation of $1.2\,\kmps$
and the peak position of $-5.9\,\kmps$. }

\label{fig:vrad_histrogram}

@@

\begin{center}\includegraphics[clip,scale=0.63]{figures/vrot_hist}\par\end{center}

\caption{Histogram of the rotational velocities ($v\,\sin{i}$) of 14 UScoOB
BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding
USco~121, a non-member). The log-normal fit (dashed) of the rotational
velocity distribution gives a standard deviation $27.8\,\kmps$ and
the peak poistion $16.9\,\kmps$.}

\label{fig:vrot_histrogram}

@@

\section{Binary fraction}

\label{sec:Binary-fraction}

In Section~\ref{sub:Radial-velocities}, we found 4 out of 17 (excluding
USco~121; non-member) objects show a statistically significant RV
variation, indicating that they are binary/multiple candidates. In
order to estimate the uncertainty in the binary/multiple fraction
from this relatively small sample, we will follow the method used
by \citet{basri:2006} who considered the binomial distribution, $P_{B}\left(x,n,p\right)$
of $x$ positive event out of $n$ trials with the probability $p$
for a positive event in each trial. In our case, $n=17$ (the number
of sample) and $x=4$. The peak of $P_{B}\left(4,17,p\right)$ curve
suggests the binary fraction of 24~per~cent, as its should be ($4/17=0.24$).
The uncertainties was estimated by plotting $P_{B}\left(4,17,p\right)$,
and finding the values of $p$ at which $P_{B}$ reduced to $e^{-1}$
of the peak value. In this analysis, we find the binary/multiple fraction
along with the uncertainties of our sample to be $f=24_{-13}^{+16}$~per~cent.

@@
